---
title: "mycourserapkg-intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mycourserapkg-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mycourserapkg)
```

# Overview

The `mycourserapkg` package provides simple, well-documented example
functions for demonstrating R package development, documentation,
testing, and continuous integration workflows.

This vignette introduces the main function in the package,
`mean_two_numbers()`, and shows how it can be used.

# The `mean_two_numbers()` function

The `mean_two_numbers()` function computes the arithmetic mean of two
numeric scalar values. It validates its inputs to ensure that both
arguments are numeric vectors of length one, and then returns their
average.

```{r example-basic}
mean_two_numbers(1, 3)
mean_two_numbers(10, 20)
mean_two_numbers(-5, 5)
```

If you pass non-numeric input or vectors with length not equal to one,
`mean_two_numbers()` will signal an error. This type of input
validation is important for robust, predictable functions.

```{r example-errors, error = TRUE}
mean_two_numbers("a", 1)
mean_two_numbers(c(1, 2), 3)
```

# Summary

In this vignette you have seen:

- How to load the `mycourserapkg` package.
- How to call `mean_two_numbers()` on valid numeric inputs.
- How the function behaves when given invalid input.

The full documentation for `mean_two_numbers()` is available in the
package help system via `?mean_two_numbers`.
